Assessing exposure to Atlantic Basin tropical storms in United States counties

### 2016-06-19 writing/DraftExposurePaper/DraftExposurePaper.Rmd
Update paper draft

all_distance <- county_distance(counties = all_counties, start_year = 1988, 
                        end_year = 2011, dist_limit = 60)

@@

```{r echo = FALSE, fig.width = 10, fig.height = 8}
top_distance_exposed <- function(storm_id){
        my_map <- map_distance_exposure(storm_id, dist_limit = 60)
        my_map <- map_tracks(storm = storm_id, plot_object = my_map, 
                             plot_points = FALSE) + 
                ggtitle(paste0(gsub("-", " (", storm_id), ")"))
}

>>>>

all_distance <- county_distance(counties = all_counties, start_year = 1988, 
                        end_year = 2011, dist_limit =100)

@@

```{r echo = FALSE, fig.width = 10, fig.height = 8}
top_distance_exposed <- function(storm_id){
        my_map <- map_distance_exposure(storm_id, dist_limit = 100)
        my_map <- map_tracks(storm = storm_id, plot_object = my_map, 
                             plot_points = FALSE) + 
                ggtitle(paste0(gsub("-", " (", storm_id), ")"))
}

### 2016-06-19 writing/DraftExposurePaper/DraftExposurePaper.tex
Update paper draft

\begin{longtable}[]{@{}lr@{}}
\caption{Top 10 storms based on the number of counties exposed, using a
metric of distance.}\tabularnewline
\toprule
Storm & \# of exposed counties\tabularnewline
\midrule
\endfirsthead
\toprule
Storm & \# of exposed counties\tabularnewline
\midrule
\endhead
Beryl (1994) & 195\tabularnewline
Frances (2004) & 194\tabularnewline
Cindy (2005) & 189\tabularnewline
Dennis (2005) & 187\tabularnewline
Chris (1988) & 181\tabularnewline
Erin (1995) & 175\tabularnewline
Allison (2001) & 170\tabularnewline
Isidore (2002) & 167\tabularnewline
Jeanne (2004) & 167\tabularnewline
Ivan (2004) & 159\tabularnewline
\bottomrule
\end{longtable}

>>>>

\begin{longtable}[]{@{}lr@{}}
\caption{Top 10 storms based on the number of counties exposed, using a
metric of distance.}\tabularnewline
\toprule
Storm & \# of exposed counties\tabularnewline
\midrule
\endfirsthead
\toprule
Storm & \# of exposed counties\tabularnewline
\midrule
\endhead
Beryl (1994) & 346\tabularnewline
Frances (2004) & 321\tabularnewline
Cindy (2005) & 317\tabularnewline
Jeanne (2004) & 296\tabularnewline
Dennis (2005) & 290\tabularnewline
Chris (1988) & 289\tabularnewline
Allison (2001) & 283\tabularnewline
Ivan (2004) & 283\tabularnewline
Erin (1995) & 280\tabularnewline
Isidore (2002) & 267\tabularnewline
\bottomrule
\end{longtable}
